### 2019-02-28 implementation.tex
add new darko paper

However, simply running a test twice in the same process (possibly with a delay between steps) does
not suffice in all cases.

@@

>>>>

Lam et al. \cite{idflakies} note that flaky tests not due to order
dependence are generally due to ``concurrency, timeouts,
network/IO, etc.'' a description that is well accounted for by our two
primary sources, and most of which can be detected, at least in
principle, by multiple runs of a test within the same testing process.  However, simply running a test twice in the same process (possibly with a delay between steps) does
not suffice in all cases.

@@

One common cause of flaky tests is \emph{test order dependence} \cite{idflakies}.  This
is less of a concern in our setting, since many problems due to test
order are easily exposed in random testing, since the
order-dependence-inducing operations will seldom usually happen in the
same order in randomly generated tests.  For example, consider the
case where a test usually run ``early'' initializes an uninitialized
value in a system, and a later test will only fail if it somehow is
run before the initializing test.  In random testing, the order of
initialization/access is likely to be random, and some run of a random
tester is likely to expose the problem as a (deterministic, not flaky) failure.

However, for cases where
there is an order dependence that is hard to translate into an
actual bug, using a fresh
process may expose such dependencies --- the ``environment'' of the
parent process will have the, e.g., flag set or value initialized, but
the new process will not.

### 2019-02-28 relatedwork.tex
add new darko paper

>>>>

iDFlakies \cite{idflakies} is a framework and dataset for flaky tests, but again focuses on whole-tests, and detecting flakiness by actually observing it.  Their work shows the order-dependence accounts for a little more than 50\% of flaky test causes, and they (like us) classify the rest as due to ``concurrency, timeouts,
network/IO, etc.' --- the kinds of cause that our approach focuses on identifying.
